Plug-and-play dual-tree algorithm runtime analysis

### 2015-10-29 bounds.tex
Fix citation type.

There exist numerous dual-tree algorithms for problems as diverse as kernel
density estimation \citep{gray2003nonparametric}, mean shift \citep{wang2007fast},
minimum spanning tree calculation \citep{march2010euclidean}, $n$-point
correlation function estimation \citep{march2012fast}, max-kernel search
\citep{curtin2013fast}, particle smoothing \citep{klaas2006fast}, variational
inference \citep{amizadeh2012variational}, range search \citep{nbody}, and
embedding techniques \cite{maaten2014accelerating}, to name a few.

>>>>

There exist numerous dual-tree algorithms for problems as diverse as kernel
density estimation \citep{gray2003nonparametric}, mean shift \citep{wang2007fast},
minimum spanning tree calculation \citep{march2010euclidean}, $n$-point
correlation function estimation \citep{march2012fast}, max-kernel search
\citep{curtin2013fast}, particle smoothing \citep{klaas2006fast}, variational
inference \citep{amizadeh2012variational}, range search \citep{nbody}, and
embedding techniques \citep{maaten2014accelerating}, to name a few.
